---
title: "Network Models"
author: "Gaurav Gade"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the libraries + functions

Load all the libraries or functions that you will use to for the rest of the assignment. It is helpful to define your libraries and functions at the top of a report, so that others can know what they need for the report to compile correctly.

```{r libaries}
##r chunk
library(gutenbergr)
library(stringr)
library(dplyr)
library(tidyr)
library(memnet)
library(jsonlite)
library(dplyr)
library(tidytext)
library(widyr)
library(ggplot2)
library(igraph)
library(ggraph)
library(tidyr)
library(memnet)


```

## The Data

Choose one of the books below. The code to download and structure the books has been provided for you, so all you would need to do is *change out* the title. 

- Book Titles:
    - Crime and Punishment
    - Pride and Prejudice
    - A Christmas Carol
    - The Iliad
    - The Art of War
    - An Inquiry into the Nature and Causes of the Wealth of Nations
    - Democracy in America — Volume 1
    - Dream Psychology: Psychoanalysis for Beginners
    - Talks To Teachers On Psychology; And To Students On Some Of Life\'s Ideals

```{r project_g}
##r chunk
##pick one book from the list above

job = read.csv("C:/Users/nagar/Documents/ANLY 540 Language Modeling/Project/Job/job_final for network.csv")


book = job[c(1,4,9)]
book = na.omit(book)

book = book %>% mutate(JobID = row_number())

book$JobRequirment = array(book$JobRequirment)
book$Title = array(book$Title)
book$JobID = array(book$JobID)

book = na.omit(book)

```

## Clean up the data

In this section, you want to create a tibble/dataframe of the individual words from your book (use by_chapter$text). Try using `unnest_tokens` (arguments shoud be word, text) and `anti_join` to create a unigram list of words without stopwords included. 

```{r}
#Tibble:

book_word <- book %>%
	unnest_tokens(word, JobRequirment) %>%
		anti_join(stop_words)


```

## Simple statistics

In this section, use the `count` function to determine the most frequent words used in the book that are not stopwords. 

```{r}

book_word %>% 
  count(word, sort = TRUE)

book %>% count(book$Title, sort = TRUE)




```

## Collocates clean up

Create a tibble/dataframe that includes the collocate pairs in the book you picked using `pairwise_count`. The document column is equivalent to id in the lecture example.

```{r}
title_word_pairs <- book_word %>% 
  pairwise_count(word, JobID, sort = TRUE, upper = FALSE)
head(title_word_pairs)


```

## Create a network plot

Create a network plot of the collocates - remember you can change the n > XX to a number that keeps a lot of the data, but filters out a lot of the smaller combinations. Set the n value in the filter function to be equal to or less than the highest n value in the word_pairs table.

```{r}
set.seed(52550)
title_word_pairs %>%
  filter(n >= 15 & n <= 16) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") + #use ?ggraph to see all the options
  geom_edge_link(aes(edge_alpha = n, edge_width = n), edge_colour = "purple") +
  geom_node_point(size = 1) +
  geom_node_text(aes(label = name), repel = TRUE, 
                 point.padding = unit(0.3, "lines")) +
  theme_void()

```

## Interpretation

What do the simple statistics and network plots tell you about the book you selected? Interpret your output in a few sentences summarizing your visualizations. 

The simple statistics and network plots reveal that the book focuses on the factors that contribute to a nation's economy and wealth. In this case, there appears to be a strong relationship between labor, produce, means, manner, time and frequently. This seems to indicate two things - agricultural output and industrial output. Then there is a relationship between proportion, manner, frequency and time which all relate to production and manufacturing timelines. The speed at which a country can manufacture goods and route them to the market for distribution is a strong indicator of a nation's competitiveness. Then we see a link between price and proportion which indicates the procing strategy and most likely how expensive goods are per unit like (price of oil per gallon or price of steel / kg etc.). The words labor, employed, people are all linked which indicates the power of a nation's service based industry. There is a link between quantity, means, trade
The most frequent words appearing in the book are  labor, produce, country, time, manner, frequently and employed all of which are important benchmarks for a country's economic output and competitiveness.




