---
title: "Word2Vec"
author: "Gaurav Gade"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the libraries + functions

Load all the libraries or functions that you will use to for the rest of the assignment. It is helpful to define your libraries and functions at the top of a report, so that others can know what they need for the report to compile correctly.

```{r libaries}
##r chunk
library(reticulate)
```

Load the Python libraries or functions that you will use for that section. 

```{python}
import pandas as pd
import numpy as np
from bs4 import BeautifulSoup
import re
from nltk.corpus import stopwords
import nltk
from sklearn.metrics import classification_report
from sklearn.metrics import accuracy_score

import nltk
import gensim
from nltk.corpus import abc

```

## The Data

The dataset is a set of Youtube comments that have been coded as:
  - 1: spam youtube messages 
  - 0: good youtube messages
  - This data is stored in the `CLASS` column

Import the data using either R or Python. I put a Python chunk here because you will need one to import the data, but if you want to first import into R, that's fine. 

```{r import data}
SOdata = read.csv("C:/Users/nagar/Documents/ANLY 540 Language Modeling/Project/Job/job_final.csv")
```

```{python}
##python chunk
SOdata = pd.read_csv("C:/Users/nagar/Documents/ANLY 540 Language Modeling/Project/Job/job_final.csv")
SOdata.head()
SOdata['JobRequirment']
```

## Clean up the data

Use one of our clean text functions to clean up the `JobRequirment` column in the dataset. 

```{python}

SOdata = r.SOdata
list_data = SOdata['JobRequirment'].tolist()

SOdata.head()
SOdata['JobRequirment']
 
# token_data = []
# 
# for sent in list_data:
#   temp = gensim.utils.simple_preprocess(sent)
#   token_data.append(temp)
#   
# token_data[0:2]

##python chunk
REPLACE_BY_SPACE_RE = re.compile('[/(){}\[\]\|@,;]') #remove symbols with space
BAD_SYMBOLS_RE = re.compile('[^0-9a-z #+_]') #take out symbols altogether
STOPWORDS = set(stopwords.words('english')) #stopwords

def clean_text(text):
    text = BeautifulSoup(text, "lxml").text # HTML decoding
    text = text.lower() # lowercase text
    text = REPLACE_BY_SPACE_RE.sub(' ', text) # replace REPLACE_BY_SPACE_RE symbols by space in text
    text = BAD_SYMBOLS_RE.sub('', text) # delete symbols which are in BAD_SYMBOLS_RE from text
    text = ' '.join(word for word in text.split() if word not in STOPWORDS) # delete stopwords from text
    return text

```

## Split the data

Split the data into testing and training data.

```{python}
##python chunk
X = SOdata['JobRequirment']
y = SOdata['IT']

from sklearn.model_selection import train_test_split
X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=0.20, random_state = 42)

```

## Process the data

For FastText OR word2vec, create the tokenized vectors of the text.

```{python}
##python chunk

tokenized_train = [nltk.tokenize.word_tokenize(text)
                   for text in X_train.to_list()]
tokenized_test = [nltk.tokenize.word_tokenize(text)
                   for text in X_test.to_list()]
```

## Build Model

Build either a word2vec or FastText model.

```{python}
##python chunk
# build word2vec model
w2v_model = gensim.models.Word2Vec(tokenized_train, 
                                   size=100, window=6,
                                   min_count=2, iter=5, workers=4)
                                   
##python chunk
from gensim.models.fasttext import FastText

# #build a fast test model
# ft_model = FastText(tokenized_train, size=100, window=6, 
#                     min_count=2, iter=5, workers=4)

```

## Convert the model

Convert the model into a set of features to use in our classifier. 

```{python}
##python chunk
##python chunk
def document_vectorizer(corpus, model, num_features):
    vocabulary = set(model.wv.index2word)
    
    def average_word_vectors(words, model, vocabulary, num_features):
        feature_vector = np.zeros((num_features,), dtype="float64")
        nwords = 0.
        
        for word in words:
            if word in vocabulary: 
                nwords = nwords + 1.
                feature_vector = np.add(feature_vector, model.wv[word])
        if nwords:
            feature_vector = np.divide(feature_vector, nwords)

        return feature_vector

    features = [average_word_vectors(tokenized_sentence, model, vocabulary, num_features)
                    for tokenized_sentence in corpus]
    return np.array(features)
    
##python chunk
# generate averaged word vector features from word2vec model
avg_wv_train_features = document_vectorizer(corpus=tokenized_train,
                                                    model=w2v_model,
                                                     num_features=100)
avg_wv_test_features = document_vectorizer(corpus=tokenized_test, 
                                                    model=w2v_model,
                                                    num_features=100)


# ##python chunk
# avg_ft_train_features = document_vectorizer(corpus=tokenized_train, model=ft_model,
#                                                      num_features=100)
# avg_ft_test_features = document_vectorizer(corpus=tokenized_test, model=ft_model,
#                                                     num_features=100)          
```

## Build a classifier model

In class, we used logistic regression to classify the data. You can use any machine learning algorithm you want here, and build a classification model. 

```{python}
##python chunk

#define your outcomes
my_tags = ["TRUE","FALSE"]

#build a log model
from sklearn.linear_model import LogisticRegression
logreg = LogisticRegression(solver='lbfgs', multi_class='auto', max_iter=10000)

#fit the data to the log model
logreg = logreg.fit(avg_wv_train_features, y_train)

# ##python chunk
# logreg = LogisticRegression(solver='lbfgs', multi_class='ovr', max_iter=10000)
# logreg = logreg.fit(avg_ft_train_features, y_train)
# y_pred = logreg.predict(avg_ft_test_features)
# print('accuracy %s' % accuracy_score(y_pred, y_test))

```

## Examine the results

Print out the accuracy, recall, and precision of your model.

```{python}
##python chunk
#predict new data
y_pred = logreg.predict(avg_wv_test_features)

#print out results
print('accuracy %s' % accuracy_score(y_pred, y_test))


print(classification_report(y_test, y_pred,target_names=my_tags))

#print(classification_report(y_test, y_pred,target_names=my_tags))
```
